---
title: "Example use of template"
title-block-banner: true
format: html
embed-resources: true
page-layout: full
toc: true
theme: 
- qcmhr.scss
---

```{r include=FALSE}

# Packages needed
pacman::p_load(
  tidyverse,
  reactable,
  reactablefmtr,
  quarto,
  plotly
)
# Set all chunks to only print output, not show code
knitr::opts_chunk$set(echo = FALSE)

# Creating list of fake data to use
example_data = list(
  # Plotly
  plotly_data = tibble(
  "Date" = dmy(paste0("01-01","-",2010:2020))
) %>% 
  mutate(
    "Mental health" = sample(1:10000,replace = F,size = n()),
    "Physical health" = sample(1:10000,replace = F,size = n()),
  ) %>% 
  pivot_longer(cols = -Date,names_to = "Health service presentation",values_to = "N"),
# Reactable data
react_data = tibble(
  "Condition" =  c( 
          "Alcohol", 
          "Cannabinoid", 
          "Nicotine", 
          "All stimulants", 
          "Opioids", 
          "Sedatives and hypnotics",
          "Multiple and other")) %>% 
  mutate(
    perc = round(abs(rnorm(n = n(),mean = 30,sd = 15)),digits = 0)
  ))

```
# Heading 1
Example of a self-contained HTML file. All that's needed to run this is a web-browser. Internet connection is needed if downloading the file (see the end)

## Heading 2
Example text by chat GPT: The old rocking chair creaked a rhythmic sigh as Amelia peered out the window. Raindrops chased each other down the glass, blurring the vibrant greens and purples of her flourishing garden. A bittersweet pang tugged at her heart. This was the same view she'd enjoyed for decades, a silent witness to countless sunrises and the changing seasons. Now, with her move to the city imminent, it felt like a cherished chapter closing.

# Results
## Table example
You can expand the tabs, there is a table in each and both are using reactable. @tbl-1 shows output that is more interactive. You can search, filter, etc. Second table is more static. More details of reactable at https://glin.github.io/reactable/ 



::: panel-tabset
### Example 1


```{r}
#| label: tbl-1
#| tbl-cap: Example of table

reactable(data = example_data$react_data,sortable = T,highlight = T,bordered = T,searchable = T,
          columns = list(
            perc = colDef(name = "Percentage of people",
                          cell = reactablefmtr::data_bars(example_data$react_data,
                                                            number_fmt = scales::number_format(suffix = "%"),
                                                            max_value = 100,
                                                            round_edges = T, fill_color = "#54B7B2",
                                                            
                       text_position = "above"))
          ))
          
```

### Example 2
```{r}
reactable(data = example_data$react_data,defaultSorted = "perc",
          defaultSortOrder = "desc",
          columns = list(
            perc = colDef(name = "Number",
                          style = color_scales(example_data$react_data, colors = viridis::viridis(5)))
          )) 
```
:::

### Figure example
@fig-1 shows what can be done using plotly. Hover over the values to see numbers, download the file etc.

```{r}
#| label: fig-1
#| fig-cap: Number of health service presentation across time

ggplotly(
  example_data$plotly_data %>% 
  ggplot(aes(x = Date,y = N,color = `Health service presentation`)) +
    geom_point() +
  geom_line() +
    labs(x = "Time", y = "Number of people") +
  theme_bw()
)
```


# Download report
Currently button below will download a QCMHR template. Can be adjusted to downloading anything
<a href="https://github.com/miiichaellam/template_QCMHR/raw/main/eg_download.pdf" class="btn btn-secondary" download="sample_report.pdf" style="width: 300px;"><i class="fa fa-download"></i> <strong style="font-weight: bold;">Click here to download report as PDF</strong></a>
